% NOTE: This is very inspired by http://www.toofishes.net/blog/latex-resume-follow-up/

\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[stretch=10]{microtype}
\usepackage{hyperref}
\usepackage{tgpagella}
\usepackage{enumitem}
\usepackage{indentfirst}
\pagestyle{empty}
\usepackage{graphicx}

\begin{document}

\begin{center}
{\huge \textbf{Pavan Raga}}

% NOTE: Alternatively could have used \hfill

\href{https://github.com/pavanraga}{www.github.com/pavanraga}\ \ \textbullet
\ \ \href{https://www.linkedin.com/in/pavanraga/}{www.linkedin.com/in/pavanraga}\ \ \textbullet
\ \ \href{mailto:pavan.raga98@gmail.com}{pavan.raga@u.nus.edu}\ \ \textbullet
\ \ {+65-98612663} \\
\ \ {463 Pasir Panjang Rd, Singapore 118797}

\end{center}

\hrule
\vspace{-1.0em}
\subsection*{About Me}
\noindent Highly skilled software engineer with more than 5 years of experience in software development and DevOps. I’m seeking a DevOps Engineer/Consultant role involving infrastructure systems or backend development. I’m passionate about immutable, reliable, automated infrastructure that scales optimally with organizational needs.
\\

\hrule
\vspace{-1.0em}
\subsection*{Work Experience}
  \begin{itemize}
    \parskip=-0.5em

    % % Dyson
    % \item[]
    % {\href{http://www.dyson.com}{\textbf{Dyson - Intelligent Machines}} \hfill
    %   \textbf{Singapore}}
    % \\
    % {\emph{Graduate Research Intern} \hfill \emph{Jan 2020 - April 2020}}

    % \begin{itemize}[label=\textbullet]
    %   \itemsep0em
    %   \item Assisted in data cleansing by creating post-processing scripts for better feature filtering and detection in robot.
    % \end{itemize}
    % Dyson Inc
    
    \item[]
    {\href{https://www.dyson.com.sg/}{\textbf{Dyson}} \hfill
      \textbf{Singapore}}
    \\
    {\emph{DevOps Engineer - Intern} \hfill \emph{Jan 2020 - Apr 2020}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Developing an internal platform to detect the best suited object detection algorithm given a data-set.
      \item Deploying the services using docker compose locally for testing and re-deploying the same to \\ managed cloud offerings such as EKS by AWS for production use.
    \end{itemize}
    \ \
    % WalletSocket Inc
    \item[]
    {\href{https://www.walletsocket.com/}{\textbf{WalletSocket - Cloud Team}} \hfill
      \textbf{Singapore}}
    \\
    {\emph{DevOps Engineer - PT} \hfill \emph{Aug 2019 - Jan 2020}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Assisted in design and architect of the Pay0k platform which is a payment gateway for merchants to accept various cryptocurrencies like bitcoin, ethereum.
      \item Responsible for developing and maintaining the CI/CD pipeline for both staging and production environments.
      \item Utilized Kubernetes extensively to orchestrate the life cycle of polyglot microservices. Followed best practices to develop manifests and integrating the same with continuous delivery.
      \item Handled increasing traffic load by scaling the backend services/container horizontally by using K8s HPA.
      \item Implemented application monitoring using Grafana/prometheus and k8s WebUI.
      \item Deployed replicated MongoDB using helm to provide high fault tolerance for the persistent layer.
    \end{itemize}
\ \
    % Cisco promotion
    \item[]
    {\href{http://www.cisco.com}{\textbf{Cisco Systems Inc}} \hfill
      \textbf{Bangalore, India}}
    \\
    {\emph{Software Engineer II} \hfill \emph{Apr 2018 - Jun 2019}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Independently worked on “Cisco-Capture” tool to enhance the debuggability in live 
      deployments by capturing control and data traffic.
      \item Moved monolothic application to configure routers to containerized
      application and deployed them in k8s cluster to provide fault tolerance.
    \end{itemize}
\ \
    % Cisco FT
    \item[]
    {\href{http://www.cisco.com}{\textbf{Cisco Systems Inc}} \hfill
      \textbf{Bangalore, India}}
    \\
    {\emph{Software Engineer I} \hfill \emph{Mar 2016 - May 2018}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Developed Layer 2 features of ASR 903 series
      of service aggregation routers.
      \item Implemented Dying Gasp support to minimise down time during power outages.
      \item Built “Autonomous Networking” feature to enable zero touch deployments. This is pull-based infrastructure as Code tool.
    \end{itemize}
\ \
    % Allgo Systems
    \item[]
    {\href{https://www.allgosystems.com/}{\textbf{AllGo Embedded Systems}} \hfill
      \textbf{Bengalore, India}}
    \\
    {\emph{Software Engineer} \hfill \emph{Jul 2014 - Feb 2016}}

    \begin{itemize}[label=\textbullet]
      \itemsep0em
      \item Part of Mirrorlink stack team, a stack which helps in replicating the
smartphones display on to car’s HMI/infotainment unit.
      \item Developed CI of software commits using Jenkins to enable fast delivery. 
      \item Built a recovery module for HMI by detecting unhealthy application in the unit and respawning them.
    \end{itemize}

  \end{itemize}


% TODO(zmanji): Revise this. Turn it into a 'Keywords' section?
% \hrule
% \vspace{-0.4em}
% \subsection*{Technical Skills}
% \begin{description}[labelindent=\parindent]
%   \item[Languages:]
%   Assembly, C, C++, Java, JavaScript, \LaTeX, Python, Ruby (on Rails)
% \end{description}

\hrule
\vspace{-1.0em}
\subsection*{Education}
  \begin{itemize}
    \parskip=-0.5em

    \item[]
    {\href{http://www.nus.edu.sg/}{\textbf{National University of Singapore (NUS)}} {GPA: 4.0/5.0} \hfill
      \textbf{Singapore}}
    \\
    {\emph{Master of Technology in Software Engineering} \hfill
      \emph{Jun 2019 - Jul 2020}}

    \begin{itemize}[label=\textbullet]
      \item Architecting Cloud Native Scalable Systems, Securing Ubiquitous Systems and Engineering Big Data
      \item Developed pay0k platform for WalletSocket and deployed into production for south korea region in Jan 2020.
    \end{itemize}

    \item[]
    {\href{https://www.nie.ac.in/}{\textbf{National Institute of Engineering (NIE)}} {GPA: 8.99/10} \hfill
      \textbf{Mysuru, India}}
    \\
    {\emph{Bachelor of Engineering in Computer Science} \hfill
      \emph{Jun 2010 - Sep 2014}}

    % \begin{itemize}[label=\textbullet]
    %   \item Related Coursework: Compilers, Programming Languages, Operating
    %     Systems, Distributed Systems.
    %   \item Created a compiler for a subset of Java 1.3 for the
    %     x86 architecture for compilers course.
    % \end{itemize}
  \end{itemize}
  
\hrule
\vspace{-1.0em}
\subsection*{Professional Certifications}
\begin{itemize}
    \parskip=-0.4em
  \item
  {\href{https://www.youracclaim.com/badges/ef62e195-5e7f-4990-aacf-3b77567e03a2}{Certified Kubernetes Administrator (CKA) Issued by: Linux Foundation}\hfill
      \textbf{Feb 2020}}
  \item
  {\href{https://www.certmetrics.com/amazon/public/badge.aspx?i=1&t=c&d=2019-04-06&ci=AWS00799157}{AWS Certified Solutions Architect(ACSAA) Issued by: AWS}\hfill
      \textbf{Apr 2019}}
\end{itemize}

\hrule
\vspace{-1.0em}
\subsection*{Keywords}
\begin{description}[labelindent=\parindent]
  \parskip=-0.4em
\item[Languages:] Python, C, YAML.
% \textbf{Have Used:} C, Python. \textbf{Want To Use:} Go.
  \item[Infrastructure:] Kubernetes, Docker, Amazon Web Service, DigitalOcean, Google Cloud Platform
  \item[Monitoring/Log:] Grafana, Prometheus, Elasticsearch, Kibana, Logstash
  \item[Tools:] Jenkins, Ansible, Jira, Wireshark, VS Code, Git, Docker, Nginx
\end{description}

\end{document}
